---
title: "Alchemist Distance Learning"
description: >
  Configuration and parameterization notes for the supervised Alchemist distance
  path.
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Alchemist Distance Learning}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", eval = FALSE)
```

Alchemist replaces empirical Gower-distance tuning with a supervised distance
learner. It starts from a prepared `Candidates` object, builds pairwise trait
features between candidate models, and trains a learner to predict transfer
error. The learned distance matrix is then used by ordination, admissibility
review, benchmarking, and policy recommendation.

Use this path when you have enough anchor diversity to learn how trait
differences map to acoustic-transfer error. When anchors are sparse, the
empirical similarity path is usually easier to diagnose because its parameters
remain direct weights and kernel settings.

```{r}
cfg <- build_configuration_template()

cfg$alchemist <- list(
  taxonomic_distance = TRUE,
  feature_type = "difference",
  distill_workers = 4,
  learner = list(
    methods = c("glm_elastic", "mars", "rf"),
    inner_folds = 3,
    workers = 4,
    seed = 20260702,
    outcome_transform = "log1p",
    lambda_rule = "lambda.1se"
  )
)

config <- build_configurer(cfg)
candidates <- build_candidates(config)
alchemist <- as_alchemist(candidates, config = config)
alchemist <- forge_distances(alchemist)
```

The `alchemist` section owns this path. `similarity` still matters because it
defines the candidate traits and coherence features available to the learner,
but empirical tuning controls in `tuning` do not control Alchemist fitting.

Key parameterization choices:

- `taxonomic_distance`: collapses family/genus/species distance into one
  continuous taxonomic feature when possible.
- `feature_type`: choose `difference` when signed standardized differences are
  meaningful; choose `gower` for bounded unsigned distances.
- `learner.methods`: use a small, defensible learner library before expanding
  to heavier models.
- `learner.inner_folds`: keep folds low when pair tables are small; larger
  values are useful only when anchor support is broad.
- `distill_workers`: controls trait-dropout sensitivity parallelism, not the
  main learner fit.

Alchemist diagnostics should focus on whether the learned distance is stable:
trait-dropout rankings, fold-level errors, and whether nearest learned donors
are scientifically plausible. If the learner overfits, simplify `methods`,
raise regularization through method-specific settings, or switch back to the
empirical similarity path until more anchor support exists.
