---
title: "Configuration Reference"
description: >
  Every configuration section and key, grouped by what it controls, with one
  copy-ready default configuration generated from the package template.
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Configuration Reference}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", eval = FALSE)

# Emit a collapsible code block with side-by-side YAML / R-list tabs.
code_drop <- function(id, yaml, r, title = "Default configuration") {
  esc <- function(x) {
    x <- gsub("&", "&amp;", x, fixed = TRUE)
    x <- gsub("<", "&lt;", x, fixed = TRUE)
    gsub(">", "&gt;", x, fixed = TRUE)
  }
  knitr::asis_output(sprintf(
'<details class="code-drop">
<summary>&#128187; %s</summary>
<div class="config-tabs">
<input class="config-tab-yaml" type="radio" name="cfg-%s" id="cfg-%s-yaml" checked>
<input class="config-tab-r" type="radio" name="cfg-%s" id="cfg-%s-r">
<div class="config-tab-labels">
<label class="config-label-yaml" for="cfg-%s-yaml">YAML</label>
<label class="config-label-r" for="cfg-%s-r">R list</label>
</div>
<div class="config-tab-panels">
<div class="config-panel config-panel-yaml">
<pre><code class="language-yaml">%s</code></pre>
</div>
<div class="config-panel config-panel-r">
<pre><code class="language-r">%s</code></pre>
</div>
</div>
</div>
</details>',
    esc(title), id, id, id, id, id, id, esc(yaml), esc(r)))
}
```

The `tsbiomass` pipeline is entirely configuration-driven. A single YAML file or
R list, validated and normalized into a `Configurer`, establishes the full
run contract before any modeling begins. This page documents every valid
section and key.

```{r}
library(tsbiomass)

# From a YAML file
cfg <- build_configurer("path/to/config.yaml")

# From the default list template (useful for scripted runs)
cfg <- build_configurer(create_configuration_template())
```

::: {.note data-title="How to read this page"}
Configuration keys are grouped by the pipeline stage they control. Every key
expands to its own dropdown describing its type and behavior. The complete set
of default values is collected in one place at the bottom of this page; see
[Default configuration](#default-configuration).
:::

<br>

# Run setup

Infrastructure settings that establish paths, runtime behavior, and caching
before any modeling begins.

## File & directory locations (`paths`)

Where the pipeline reads inputs and writes outputs. Set these once; everything
else resolves relative to them.

<details>
<summary>Parameters</summary>

<details class="cfg-key">
<summary><code>input_file</code>: primary study workbook</summary>

*string · **required***: The `.xlsx` workbook holding your study metadata and
candidate models. External YAML alias: `input`.

</details>

<details class="cfg-key">
<summary><code>out_root</code>: root output folder</summary>

*string · **required***: Root directory under which all products are written.
External YAML alias: `output_root`.

</details>

<details class="cfg-key">
<summary><code>cache_dir</code>: default cache folder</summary>

*string · **required***: Base folder for cached intermediate products.
External YAML alias: `cache_folder`.

</details>

<details class="cfg-key">
<summary><code>supplemental_dir</code>: supplemental trait files</summary>

*string*: Folder containing supplemental trait files referenced by `data`
sources. External YAML alias: `support_folder`.

</details>

<details class="cfg-key">
<summary><code>log_file</code>: log-file path</summary>

*string*: Where progress and error messages are written. Used only when
`execution.write_log = true`. External YAML alias: `log_path`.

</details>

</details>

## Runtime behavior (`execution`)

Global switches that change how the pipeline runs, independent of any single
modeling stage.

<details><summary>Parameters</summary>
<details class="cfg-key">
<summary><code>strict_length_pdf</code>: require finite length support</summary>

*logical*: When `true`, models with missing length-support bounds are excluded
from PDF construction rather than back-filled. External YAML alias: `strict_pdf`.

</details>

<details class="cfg-key">
<summary><code>run_multiplier_model</code>: enable biomass-multiplier branch</summary>

*logical*: Enables the biomass-multiplier workflow branch. External YAML alias:
`run_multiplier`.

</details>

<details class="cfg-key">
<summary><code>write_log</code>: write a run log</summary>

*logical*: Writes progress and error messages to `paths.log_file`.

</details>

<details class="cfg-key">
<summary><code>progress</code>: progress messages</summary>

*logical*: Enables package progress messages globally. Individual function
arguments can still override this for one call.

</details>

</details>

## Caching (`cache`)

Controls where intermediate products are stored and when they are recomputed.
Each expensive stage caches its result; a global `refresh` (or per-stage
override) forces recomputation.

<details><summary>Parameters</summary>

<details class="cfg-key">
<summary><code>folder</code>: base cache folder</summary>

*string*: Base folder for all cache files.

</details>

<details class="cfg-key">
<summary><code>refresh</code>: global recompute switch</summary>

*logical*: When `true`, every cached product is recomputed. Individual sections
can override this with their own `refresh`.

</details>

<details class="cfg-key">
<summary><code>names</code>: per-product filename overrides</summary>

*named list*: Override the filename used for any cached product. Valid keys:

| Key | Product |
|-----|---------|
| `worms` | WoRMS taxonomy pull |
| `fishbase` | FishBase trait pull |
| `pelagic` / `azores` / `continental` | Regional trait tables |
| `mstraits` | Morphometric/soft-tissue traits |
| `species_enriched` | Enriched species table |
| `candidate_models` | Prepared candidate pool |
| `similarity_tuning` | Similarity-tuning results |
| `anchor_admissibility` | Anchor admissibility screen |
| `policy_benchmark` | Policy benchmark |
| `policy_conformal` | Conformal calibration |
| `policy_selection` | Selected policies |
| `policy_sensitivity` | Sensitivity simulation |

</details>

<details class="cfg-key">
<summary><code>defaults_path</code>: custom cache-defaults JSON</summary>

*string*: Path to a custom cache-defaults JSON file, replacing the packaged
defaults.

</details>

</details>

# Candidate data

Trait sources and the candidate pool assembled from them.

## Trait data sources (`data`)

Declares the trait datasets fed into candidate enrichment. Each entry is one
dataset; at minimum you need a `study_metadata` entry pointing at your study
workbook. Built-in IDs are back-filled automatically.

<details><summary>Parameters</summary>

<details class="cfg-key">
<summary><code>id</code>: dataset identifier</summary>

*string · **required***: Case-insensitive dataset identifier. Built-in IDs:
`study_metadata`, `worms`, `fishbase`, `pelagic` / `pelagictraits`,
`azores` / `azorestraits`, `continental` / `continentaltraits`, `mstraits`.

</details>

<details class="cfg-key">
<summary><code>alias</code>: alternate slug</summary>

*string*: Alternate slug usable in `candidates.enrich.precedence`.

</details>

<details class="cfg-key">
<summary><code>type</code>: source type descriptor</summary>

*string*: External type descriptor (e.g. `single_file`, `directory`).
Back-filled for built-in IDs.

</details>

<details class="cfg-key">
<summary><code>engine</code>: read engine</summary>

*string*: Engine descriptor (e.g. `r_package`, `rdata`). Back-filled for
built-in IDs.

</details>

<details class="cfg-key">
<summary><code>path</code>: file or folder path</summary>

*string*: File or folder path. Required for sources that read from disk.

</details>

<details class="cfg-key">
<summary><code>cache_path</code>: per-source cache override</summary>

*string*: Explicit cache-path override for this source.

</details>

<details class="cfg-key">
<summary><code>refresh</code>: per-source refresh</summary>

*logical*: Per-source refresh override.

</details>

</details>

## Candidate pool (`candidates`)

Orchestrates how the candidate pool is enriched, prepared, and anchored on top
of the declared `data` sources.

<details><summary>Parameters</summary>

<details class="cfg-key">
<summary><code>enrich</code>: trait enrichment</summary>

Merges trait sources into a single enriched species table.

<details class="cfg-key">
<summary><code>precedence</code></summary>

*character vector*: Source priority order during enrichment. May use normalized
`id` or `alias`. Example: `[study_metadata, fishbase, worms]`.

</details>

<details class="cfg-key">
<summary><code>missing_tokens</code></summary>

*character vector*: Values treated as missing. Example: `["-9999", "unknown"]`.

</details>

<details class="cfg-key">
<summary><code>cache_path</code></summary>

*string*: Explicit cache override for the enriched species table.

</details>

</details>

<details class="cfg-key">
<summary><code>prepare</code>: candidate preparation</summary>

Normalizes the enriched table into the prepared candidate pool.

<details class="cfg-key">
<summary><code>missing_tokens</code></summary>

*character vector*: Missing-value tokens applied during trait preparation.

</details>

<details class="cfg-key">
<summary><code>cache_path</code></summary>

*string*: Explicit cache override for the prepared candidate table.

</details>

<details class="cfg-key">
<summary><code>refresh</code></summary>

*logical*: Per-stage refresh override.

</details>

</details>

<details class="cfg-key">
<summary><code>anchors</code>: reference-anchor selection</summary>

Settings passed to `set_reference_anchors()`. Choose anchors either dynamically
with `selector` or explicitly with `model_ids`.

<details class="cfg-key">
<summary><code>selector</code></summary>

*named list*: Dynamic filter over candidate columns. Each key is a column and
each value the required match. Common filter columns:

| Column | Selects by |
|--------|-----------|
| `regional_body` | Managing body / survey program (e.g. `SWFSC`) |
| `ocean_basin` | Ocean basin |
| `fao` | FAO major area |
| `species` / `genus` / `family` | Taxonomic level |
| `season` | Survey season |

Example: `{regional_body: SWFSC}`.

</details>

<details class="cfg-key">
<summary><code>model_ids</code></summary>

*character vector*: Explicit anchor model IDs (alternative to `selector`).

</details>

<details class="cfg-key">
<summary><code>model_id_col</code></summary>

*string*: Column name holding anchor IDs when using `model_ids`.

</details>

<details class="cfg-key">
<summary><code>require_selection</code></summary>

*logical*: Whether zero matches should raise an error.

</details>

</details>

</details>

# Similarity distances

How donor-target relatedness is learned, weighted, tuned, and visualized. See
the [Super Learners](super-learners.html) documentation for guidance on learner
choices.

## Supervised distance learner (`alchemist`)

Settings for the `Alchemist` supervised distance learner, which turns per-trait
pairwise distances into the acoustic-distance matrix. Trait names default to
those in `similarity` when not specified here.

<details><summary>Parameters</summary>

<details class="cfg-key">
<summary><code>feature_type</code>: pairwise feature representation</summary>

*string*: How a donor-anchor pair is encoded as features. Options: `"gower"`
(unsigned Gower distances), `"difference"` (signed standardized differences),
`"mahalanobis"` (squared standardized differences).

</details>

<details class="cfg-key">
<summary><code>taxonomic_distance</code>: collapse taxonomy to one distance</summary>

*logical*: Replace individual family/genus/species Gower features with a single
continuous phylogenetic distance (Open Tree of Life, with rank-based fallback).

</details>

<details class="cfg-key">
<summary><code>species_traits</code>: species pair-level features</summary>

*character vector · default from `similarity`*: Species-level traits used as
pair-level features for the distance learner.

</details>

<details class="cfg-key">
<summary><code>study_traits</code>: study pair-level features</summary>

*character vector · default from `similarity`*: Study-level traits used as
pair-level features for the distance learner.

</details>

<details class="cfg-key">
<summary><code>distill_workers</code>: sensitivity worker count</summary>

*integer*: Worker count for sigma-dropout sensitivity in `distill_traits()`.

</details>

<details class="cfg-key">
<summary><code>learner</code>: Super Learner library</summary>

Controls the stacked ensemble trained inside `forge_distances()`. See
`list_learners()` for valid method names.

<details class="cfg-key">
<summary><code>methods</code></summary>

*character vector*: Base learner methods in the library.

</details>

<details class="cfg-key">
<summary><code>inner_folds</code></summary>

*integer*: Inner cross-validation folds for out-of-fold predictions.

</details>

<details class="cfg-key">
<summary><code>seed</code></summary>

*integer*: Reproducibility seed.

</details>

<details class="cfg-key">
<summary><code>outcome_transform</code></summary>

*string*: Transform applied to the acoustic-distance outcome before fitting.
Options: `"identity"`, `"log1p"`, `"sqrt"`.

</details>

<details class="cfg-key">
<summary><code>lambda_rule</code></summary>

*string*: Penalized-model lambda selection. Options: `"min"` (`lambda.min`),
`"1se"` (`lambda.1se`).

</details>

<details class="cfg-key">
<summary><code>oof_mode</code></summary>

*string*: Out-of-fold split strategy. `"anchor_species"` groups by anchor
species; `"species_purged"` excludes both anchor and donor species from
training.

</details>

<details class="cfg-key">
<summary><code>workers</code></summary>

*integer*: Parallel worker count for multi-method fitting.

</details>

<details class="cfg-key">
<summary><code>method_settings</code></summary>

*named list*: Per-method hyper-parameter overrides for the base learners in
`methods`. Each top-level key is a public learner method name; supply only the
fields you want to change. Parameter names and defaults are documented per method
in the Alchemist section of the
[Super Learners vignette](super-learners.html#alchemist).

</details>

</details>

</details>

## Similarity matrix (`similarity`)

Trait selection, coherence, and kernel settings for the similarity matrix. This
section defines the baseline distance surface. Empirical search ranges and
resampling controls live in [`tuning`](#similarity-tuning-tuning); the
supervised Alchemist path is described in [Alchemist distance learning](alchemist-distance-learning.html).

<details><summary>Parameters</summary>

<details class="cfg-key">
<summary><code>alpha</code>: species-vs-study blend</summary>

*number*: Blend between species and study distances. `1.0` = species only,
`0.0` = study only.

</details>

<details class="cfg-key">
<summary><code>kernel_scale</code>: kernel concentration</summary>

*number*: Global kernel scale. Higher values concentrate weight on nearer
donors.

</details>

<details class="cfg-key">
<summary><code>species_traits</code>: species traits in the distance</summary>

*character vector or named list*: Species-level traits included in distance
computation. The named-list form sets per-trait starting weights, e.g.
`{length: 1.0, depth: 0.5}`.

</details>

<details class="cfg-key">
<summary><code>study_traits</code>: study traits in the distance</summary>

*character vector or named list*: Study-level traits included in distance
computation. The named-list form sets per-trait starting weights.

</details>

<details class="cfg-key">
<summary><code>conformal_alpha</code>: interval miscoverage target</summary>

*number*: Target miscoverage level for conformal interval calibration.

</details>

<details class="cfg-key">
<summary><code>core_weight_cutoff</code>: high-support donor threshold</summary>

*number*: Similarity-weight threshold for identifying high-support donor
subsets.

</details>

<details class="cfg-key">
<summary><code>cache_path</code>: cache override</summary>

*string*: Explicit cache-path override for the similarity matrix.

</details>

<details class="cfg-key">
<summary><code>refresh</code>: force recompute</summary>

*logical*: Force recompute of the similarity cache.

</details>

<details class="cfg-key">
<summary><code>coherence</code>: measurement-overlap features</summary>

Measurement-overlap features supplementing trait distances.

<details class="cfg-key">
<summary><code>length</code></summary>

Length-overlap coherence feature.

- `mode` *(string)*: `overlap`, `literal`, or `none`.
- `weight` *(number)*: Feature weight.

</details>

<details class="cfg-key">
<summary><code>depth</code></summary>

Depth-overlap coherence feature.

- `mode` *(string)*: `overlap`, `literal`, or `none`.
- `weight` *(number)*: Feature weight.

</details>

<details class="cfg-key">
<summary><code>frequency</code></summary>

Acoustic-frequency-overlap coherence feature.

- `mode` *(string)*: `overlap`, `literal`, or `none`.
- `weight` *(number)*: Feature weight.
- `gap` *(number)*: Maximum frequency gap (kHz) treated as overlapping under
  `mode: overlap`.

</details>

</details>

</details>

## Similarity tuning (`tuning`)

Hyper-parameters for the empirical similarity-tuning search over trait weights,
coherence weights, `alpha`, and `kernel_scale`. These settings apply to
`tune_similarities()` and the empirical Candidates path described in
[Empirical similarity tuning](empirical-similarity-tuning.html).

<details><summary>Parameters</summary>

<details class="cfg-key">
<summary><code>max_models_per_species</code>: models per species in subsets</summary>

*integer*: Maximum retained models per species in tuning subsets. External YAML
alias: `species_model_limit`.

</details>

<details class="cfg-key">
<summary><code>n_resamples</code>: empirical resamples</summary>

*integer*: Number of empirical tuning resamples. External YAML alias:
`resamples`.

</details>

<details class="cfg-key">
<summary><code>n_cores</code>: worker count</summary>

*integer*: Worker count for tuning runs.

</details>

<details class="cfg-key">
<summary><code>seed</code>: reproducibility seed</summary>

*integer*: Reproducibility seed.

</details>

<details class="cfg-key">
<summary><code>alpha_range</code>: alpha search bounds</summary>

*`{from, to}`*: Empirical tuning bounds for the species-versus-study blend.

</details>

<details class="cfg-key">
<summary><code>kernel_scale_range</code>: kernel-scale search bounds</summary>

*`{from, to}`*: Empirical tuning bounds for the global kernel scale.

</details>

<details class="cfg-key">
<summary><code>coherence</code>: coherence-weight search bounds</summary>

*named list*: Optional empirical tuning bounds for coherence weights. Supported
entries are `length.range`, `depth.range`, and `frequency.range`, each as
`{from, to}`.

</details>

<details class="cfg-key">
<summary><code>grid_refinement_levels</code>: local refinement passes</summary>

*integer*: Local search-refinement passes after the coarse grid.

</details>

<details class="cfg-key">
<summary><code>response_surface_top_n</code>: retained candidate points</summary>

*integer*: Candidate points kept during response-surface refinement.

</details>

<details class="cfg-key">
<summary><code>rmse_tolerance</code>: convergence tolerance</summary>

*number*: RMSE improvement below which refinement is considered converged.

</details>

<details class="cfg-key">
<summary><code>support_strata_bins</code>: support strata</summary>

*integer*: Number of support strata used when balancing tuning resamples.

</details>

<details class="cfg-key">
<summary><code>regularization</code>: search regularization</summary>

*named list*: Regularization strengths that keep the tuned parameters near
their priors. Fields: `alpha`, `kernel_scale`, `coherence_scale`, `stability`.

</details>

<details class="cfg-key">
<summary><code>equal_start_weights</code>: equal initial trait weights</summary>

*logical*: Initialize all trait weights equally rather than using configured
magnitudes as priors.

</details>

</details>

## Ordination (`ordination`)

NMDS ordination settings, applied after `forge_distances()` to visualize proxy
model diversity.

<details><summary>Parameters</summary>

<details class="cfg-key">
<summary><code>include_loadings</code>: envfit vector loadings</summary>

*logical*: Include envfit vector loadings in the ordination output.

</details>

<details class="cfg-key">
<summary><code>include_centroids</code>: factor-level centroids</summary>

*logical*: Include factor-level centroids.

</details>

<details class="cfg-key">
<summary><code>nmds_args</code>: metaMDS arguments</summary>

*named list*: Arguments forwarded to `vegan::metaMDS()`.

</details>

<details class="cfg-key">
<summary><code>envfit_args</code>: envfit arguments</summary>

*named list*: Arguments forwarded to `vegan::envfit()`.

</details>

</details>

# Policies & admissibility

Which transfer paths are admissible, which policies are declared, and how they
are benchmarked.

## Admissibility gates (`admissibility`)

Hard binary gates that exclude transfer paths before any policy is applied.
Donors that fail a check are removed from the candidate pool for the affected
target.

<details><summary>Parameters</summary>

<details class="cfg-key">
<summary><code>species_traits</code>: species exact-match gates</summary>

*character vector*: Categorical or binary species traits that must match
exactly between donor and target.

</details>

<details class="cfg-key">
<summary><code>study_traits</code>: study exact-match gates</summary>

*character vector*: Study-level traits used as exact-match gates.

</details>

<details class="cfg-key">
<summary><code>key_metadata_max</code>: missingness tolerance</summary>

*number*: Maximum tolerated missing fraction across key study-level metadata
fields.

</details>

<details class="cfg-key">
<summary><code>cache_path</code>: cache override</summary>

*string*: Explicit cache-path override for the admissibility screen.

</details>

<details class="cfg-key">
<summary><code>refresh</code>: force recompute</summary>

*logical*: Force recompute of the admissibility cache.

</details>

<details class="cfg-key">
<summary><code>coherence</code>: measurement-overlap gates</summary>

Minimum measurement-overlap requirements applied as gates.

<details class="cfg-key">
<summary><code>length</code></summary>

Length-overlap gate.

- `mode` *(string)*: `overlap`, `literal`, or `none`.
- `min` *(number)*: Minimum required fractional length overlap.

</details>

<details class="cfg-key">
<summary><code>depth</code></summary>

Depth-overlap gate.

- `mode` *(string)*: `overlap`, `literal`, or `none`.
- `min` *(number)*: Minimum required fractional depth overlap.

</details>

<details class="cfg-key">
<summary><code>frequency</code></summary>

Frequency-overlap gate.

- `mode` *(string)*: `none`, `literal`, or `overlap`.
- `gap` *(number)*: Gap threshold (kHz) under `mode: overlap`.

</details>

</details>

</details>

## Transfer policies (`policies`)

Declares the transfer policies to benchmark. Use the **constructor form**
(`metric` + `slope_class` + `group`) to generate named policy sets from the registry,
or the **explicit form** (`active`) to list policy names directly.

<details><summary>Parameters</summary>

<details class="cfg-key">
<summary><code>metric</code>: donor-aggregation metric filter</summary>

*character vector*: Global metric filter. Supported: `closest`, `weighted_mean`,
`unweighted_mean`, `survey_distance`, `taxon_distance`, `species_distance`,
`random`.

</details>

<details class="cfg-key">
<summary><code>slope_class</code>: slope-class filter</summary>

*character vector*: Slope classes. Supported: `all`, `fixed_slope`,
`free_slope`.

</details>

<details class="cfg-key">
<summary><code>group</code>: per-grouping overrides</summary>

*named list*: One entry per donor-pool grouping (e.g. `species`, `genus`,
`family`). Each value configures per-group overrides:

<details class="cfg-key">
<summary><code>group.&lt;name&gt;.include_base</code></summary>

*logical*: When `joint` variants are listed, keep the plain root group as well.

</details>

<details class="cfg-key">
<summary><code>group.&lt;name&gt;.metric</code></summary>

*character vector*: Per-group metric override.

</details>

<details class="cfg-key">
<summary><code>group.&lt;name&gt;.joint</code></summary>

*list*: One or more trait names to conjoin with the root group key. Each entry
becomes a separate `<group>_<trait>` policy variant.

</details>

</details>

<details class="cfg-key">
<summary><code>active</code>: explicit policy list</summary>

*character vector*: Explicit policy name strings (explicit form). Example:
`[species_closest_all, genus_weighted_mean_all]`.

</details>

</details>

## Policy benchmarking (`benchmark`)

Settings for the policy-benchmarking stage, which scores each policy against the
reference anchors.

<details><summary>Parameters</summary>

<details class="cfg-key">
<summary><code>workers</code>: parallel anchor evaluation</summary>

*integer*: Worker count for parallel anchor evaluation.

</details>

<details class="cfg-key">
<summary><code>engine</code>: evaluation backend</summary>

*string*: `"cpp"` uses the compiled C++ backend; `"r"` uses the pure-R path.

</details>

<details class="cfg-key">
<summary><code>include_ts_error</code>: TS reconstruction error</summary>

*logical*: Include TS-curve reconstruction error in benchmark outputs.

</details>

<details class="cfg-key">
<summary><code>cache_path</code>: cache override</summary>

*string*: Explicit cache-path override for the benchmark.

</details>

<details class="cfg-key">
<summary><code>refresh</code>: force recompute</summary>

*logical*: Force recompute of the benchmark cache.

</details>

</details>

# Uncertainty & policy selection

The two post-benchmark Super Learners: one calibrates prediction-interval widths,
the other selects policies and powers the meta-learner. See the
[Super Learners vignette](super-learners.html).

## Conditional uncertainty (`uncertainty`)

Trains a cross-fitted model to predict expected absolute log-error, used to
calibrate prediction-interval widths.

<details><summary>Parameters</summary>

<details class="cfg-key">
<summary><code>method</code>: learner method</summary>

*string*: `"glm"` for a single generalized linear model, or `"super_learner"`
to enable stacked-ensemble mode.

</details>

<details class="cfg-key">
<summary><code>super_methods</code>: ensemble library</summary>

*character vector*: Base learner library used when `method = "super_learner"`.

</details>

<details class="cfg-key">
<summary><code>n_folds</code>: outer folds</summary>

*integer*: Outer cross-fitting folds.

</details>

<details class="cfg-key">
<summary><code>inner_folds</code>: inner folds</summary>

*integer*: Inner folds for penalized learners.

</details>

<details class="cfg-key">
<summary><code>workers</code>: cross-fitting workers</summary>

*integer*: Worker count for cross-fitting.

</details>

<details class="cfg-key">
<summary><code>outcome_col</code>: regression target</summary>

*string*: Benchmark column used as the regression target.

</details>

<details class="cfg-key">
<summary><code>outcome_clip_quantile</code>: extreme-outcome clipping</summary>

*number*: Upper quantile used to clip extreme training outcomes.

</details>

<details class="cfg-key">
<summary><code>outcome_transform</code>: outcome transform</summary>

*string*: Transform applied to the outcome before fitting.

</details>

<details class="cfg-key">
<summary><code>lambda_rule</code>: lambda selection rule</summary>

*string*: Lambda selection rule for penalized learners.

</details>

<details class="cfg-key">
<summary><code>loss</code>: combiner loss</summary>

*string*: Super-learner combiner loss. Must be `"squared_error"` with NNLS.

</details>

<details class="cfg-key">
<summary><code>method_settings</code>: per-method overrides</summary>

*named list*: Per-method hyper-parameter overrides for the base learners in
`super_methods`. Each top-level key is a public learner method name; supply only
the fields you want to change.
Parameter names and defaults are documented per method in the Uncertainty
section of the
[Super Learners vignette](super-learners.html#learner-2-uncertainty-uncertainty).

</details>

<details class="cfg-key">
<summary><code>cache_path</code>: cache override</summary>

*string*: Explicit cache-path override for the uncertainty learner.

</details>

<details class="cfg-key">
<summary><code>refresh</code>: force recompute</summary>

*logical*: Force recompute of the uncertainty cache.

</details>

</details>

## Policy selection & meta-learner (`selection`)

Post-benchmarking policy selection, plus the optional meta-learner used by
`PolicyLearner`. The policy-selection keys are listed first; the meta-learner
keys mirror `uncertainty`.

<details><summary>Parameters</summary>

<details class="cfg-key">
<summary><code>one_se_multiplier</code>: one-SE screen width</summary>

*number*: Multiplier on the best policy's standard error for the one-SE screen.

</details>

<details class="cfg-key">
<summary><code>equivalence_tolerance</code>: practical-equivalence band</summary>

*number*: Practical tolerance for pairwise equivalence summaries.

</details>

<details class="cfg-key">
<summary><code>n_boot</code>: bootstrap replicates</summary>

*integer*: Bootstrap replicates for selection uncertainty.

</details>

<details class="cfg-key">
<summary><code>seed</code>: selection seed</summary>

*integer*: Reproducibility seed for selection.

</details>

<details class="cfg-key">
<summary><code>uncertainty_rule</code>: final width filter</summary>

*string*: `"min"` keeps only the narrowest interval; `"tolerance"` keeps widths
within the configured absolute/relative band; `"one_se"` uses the one-SE screen.

</details>

<details class="cfg-key">
<summary><code>u_tol_rel</code>: relative width tolerance</summary>

*number*: Relative width tolerance (fraction of minimum width) under
`uncertainty_rule = tolerance`.

</details>

<details class="cfg-key">
<summary><code>u_tol_abs</code>: absolute width tolerance</summary>

*number*: Absolute log-width tolerance under `uncertainty_rule = tolerance`.

</details>

<details class="cfg-key">
<summary><code>conformal_alpha</code>: post-selection miscoverage</summary>

*number*: Miscoverage level for post-selection conformal calibration.

</details>

<details class="cfg-key">
<summary><code>method</code>: meta-learner method</summary>

*string*: Meta-learner method used by `PolicyLearner`. `"glm"` or
`"super_learner"` for ensemble mode.

</details>

<details class="cfg-key">
<summary><code>super_methods</code>: meta-learner library</summary>

*character vector*: Base learner library when `method = "super_learner"`.

</details>

<details class="cfg-key">
<summary><code>n_folds</code>: outer folds</summary>

*integer*: Outer cross-fitting folds for the meta-learner.

</details>

<details class="cfg-key">
<summary><code>inner_folds</code>: inner folds</summary>

*integer*: Inner folds for penalized meta-learners.

</details>

<details class="cfg-key">
<summary><code>workers</code>: cross-fitting workers</summary>

*integer*: Cross-fitting worker count for the meta-learner.

</details>

<details class="cfg-key">
<summary><code>outcome_col</code>: learner target</summary>

*string*: Benchmark column used as the meta-learner target.

</details>

<details class="cfg-key">
<summary><code>outcome_transform</code>: outcome transform</summary>

*string*: Transform applied to the meta-learner outcome before fitting.

</details>

<details class="cfg-key">
<summary><code>lambda_rule</code>: lambda selection rule</summary>

*string*: Lambda selection rule for penalized meta-learners.

</details>

<details class="cfg-key">
<summary><code>loss</code>: combiner loss</summary>

*string*: Meta-learner combiner loss. Must be `"squared_error"` with NNLS.

</details>

<details class="cfg-key">
<summary><code>method_settings</code>: per-method overrides</summary>

*named list*: Per-method hyper-parameter overrides for the meta-learner base
learners. Each top-level key is a public learner method name; supply only the
fields you want to change. Parameter names and defaults are documented per method in the
Selection section of the
[Super Learners vignette](super-learners.html#learner-3-selection-policylearner-selection).

</details>

<details class="cfg-key">
<summary><code>cache_path</code>: cache override</summary>

*string*: Explicit cache-path override for selection.

</details>

<details class="cfg-key">
<summary><code>refresh</code>: force recompute</summary>

*logical*: Force recompute of the selection cache.

</details>

</details>

# Validation & sensitivity

Outer-loop holdout validation and scenario-based sensitivity analysis.

## Outer-loop validation (`sentinel`)

Outer-loop holdout validation and ablation settings for `build_sentinel()` /
`run_sentinel()`.

<details><summary>Parameters</summary>

<details class="cfg-key">
<summary><code>baseline_species_folds</code>: headline validation folds</summary>

*integer*: Species-disjoint outer folds for the headline validation run. Set to
the total species count for full leave-one-species-out.

</details>

<details class="cfg-key">
<summary><code>ablation_species_folds</code>: folds per ablation</summary>

*integer*: Folds used per ablation scenario.

</details>

<details class="cfg-key">
<summary><code>workers</code>: outer worker count</summary>

*integer*: Outer workflow worker count.

</details>

<details class="cfg-key">
<summary><code>batch_size</code>: checkpoint batch size</summary>

*integer*: Workflows checkpointed per batch.

</details>

<details class="cfg-key">
<summary><code>include_ts_error</code>: TS error in fold benchmarks</summary>

*logical*: Include TS-curve error in fold-local benchmarks.

</details>

<details class="cfg-key">
<summary><code>throttle_inner_workers</code>: prevent oversubscription</summary>

*logical*: Prevent inner workers from oversubscribing cores allocated to outer
workers.

</details>

<details class="cfg-key">
<summary><code>fast_validation</code>: reduced NMDS schedule</summary>

*logical*: Reduce the NMDS schedule for faster runs.

</details>

<details class="cfg-key">
<summary><code>logging</code>: file logging</summary>

*logical*: Enable fold-level file logging.

</details>

<details class="cfg-key">
<summary><code>save_case_artifacts</code>: persist fold artifacts</summary>

*logical*: Persist fold-level RDS artifacts for debugging.

</details>

</details>

## Sensitivity simulation (`simulation`)

Settings for `PolicySimulator` sensitivity runs, which rerun benchmarking across
perturbed scenarios.

<details><summary>Parameters</summary>

<details class="cfg-key">
<summary><code>workers</code>: worker count</summary>

*integer*: Worker count for scenario reruns.

</details>

<details class="cfg-key">
<summary><code>cache_path</code>: cache override</summary>

*string*: Explicit cache-path override for the sensitivity simulation.

</details>

<details class="cfg-key">
<summary><code>refresh</code>: force recompute</summary>

*logical*: Force recompute of the sensitivity cache.

</details>

</details>

# Default configuration

The complete default configuration produced by
`create_configuration_template()`, shown in YAML and R-list form. Every value
below is the packaged default; override only the keys you need.

```{r cd-default, echo=FALSE, results='asis', eval=TRUE}
# Default config generated verbatim from create_configuration_template(); regenerate if the template changes.
code_drop("default",
  yaml = r"--(paths:
  input_file: input.xlsx
  out_root: outputs
  cache_dir: cache
  supplemental_dir: supplemental
  log_file: outputs/tsbiomass_run.log
execution:
  strict_length_pdf: false
  run_multiplier_model: false
  write_log: false
  progress: false
tuning:
  max_models_per_species: 2
  n_resamples: 8
  n_cores: 1
  seed: ~
  alpha_range:
    from: 0.1
    to: 0.9
  kernel_scale_range:
    from: 1.0
    to: 8.0
  coherence:
    length:
      range:
        from: 0.5
        to: 6.0
    depth:
      range:
        from: 0.5
        to: 6.0
    frequency:
      range:
        from: 0.5
        to: 6.0
  grid_refinement_levels: 1
  response_surface_top_n: 20
  rmse_tolerance: 0.01
  support_strata_bins: 4
  regularization:
    alpha: 0.05
    kernel_scale: 0.05
    coherence_scale: 0.05
    stability: 0.02
  equal_start_weights: false
similarity:
  alpha: 0.8
  kernel_scale: 4.0
  species_traits:
    class: 1.0
  study_traits:
    fao_area: 1.0
  coherence:
    length:
      mode: overlap
      weight: 2.0
    depth:
      mode: overlap
      weight: 3.0
    frequency:
      mode: overlap
      weight: 2.0
      gap: 60.0
  conformal_alpha: 0.1
ordination:
  include_loadings: false
  include_centroids: false
policies:
  group:
  - species
  metric:
  - closest
  slope_class:
  - all
cache:
  folder: cache
  refresh: false
  names:
    worms: worms_species_traits.rds
    fishbase: fishbase_species_traits.rds
    pelagic: pelagic_species_traits.rds
    azores: azores_species_traits.rds
    continental: continental_species_traits.rds
    mstraits: mstraits_species_traits.rds
    species_enriched: species_traits_enriched.rds
    candidate_models: candidate_models_prepared.rds
    similarity_tuning: similarity_tuning.rds
    anchor_admissibility: anchor_admissibility.rds
    policy_benchmark: policy_benchmark.rds
    policy_conformal: policy_conformal.rds
    policy_selection: policy_selection.rds
    policy_sensitivity: policy_sensitivity.rds
benchmark:
  workers: 1
  engine: cpp
  include_ts_error: false
admissibility:
  species_traits: []
  study_traits: []
  coherence:
    length:
      mode: overlap
      min: 0.25
    depth:
      mode: overlap
      min: 0.25
    frequency:
      mode: none
      gap: 60.0
  key_metadata_max: 0.25
uncertainty:
  method: glm
  super_methods: ~
  method_settings:
    glm: []
    glm_ridge:
      standardize: true
      type_measure: mae
      alpha: 0
    glm_lasso:
      standardize: true
      type_measure: mae
      alpha: 1
    glm_elastic:
      standardize: true
      type_measure: mae
      alpha: 0.25
    qreg:
      tau: 0.5
      fit_method: fn
    gam:
      fit_method: REML
      select_terms: true
    lmm:
      fit_method: REML
      random_intercept: .split_group
    rpart:
      cp: 0.01
      minsplit: 20
      minbucket: 7
      maxdepth: 30
    rf:
      num_trees: 500
      mtry: ~
      min_node_size: 5
      max_depth: ~
      sample_fraction: 1
      replace: true
      respect_unordered_factors: order
    xgboost:
      nrounds: 100
      eta: 0.3
      max_depth: 6
      min_child_weight: 1
      subsample: 1
      colsample_bytree: 1
      lambda: 1
      alpha: 0
      nthread: 1
    mars:
      degree: 2
      penalty: 3
      nprune: ~
      pmethod: backward
    bart:
      num_trees: 75
      alpha: 0.95
      beta: 2
      min_samples_leaf: 5
      max_depth: 10
      keep_gfr: true
      variance_forest_num_trees: 50
      random_effects_group: .split_group
      num_gfr: 0
      num_burnin: 100
      num_mcmc: 200
      variance_forest: false
      random_effects: false
    xbart:
      num_trees: 75
      alpha: 0.95
      beta: 2
      min_samples_leaf: 5
      max_depth: 10
      keep_gfr: true
      variance_forest_num_trees: 50
      random_effects_group: .split_group
      num_gfr: 40
      num_burnin: 0
      num_mcmc: 0
      variance_forest: false
      random_effects: false
    wsbart:
      num_trees: 75
      alpha: 0.95
      beta: 2
      min_samples_leaf: 5
      max_depth: 10
      keep_gfr: true
      variance_forest_num_trees: 50
      random_effects_group: .split_group
      num_gfr: 20
      num_burnin: 0
      num_mcmc: 200
      variance_forest: false
      random_effects: false
    vfbart:
      num_trees: 75
      alpha: 0.95
      beta: 2
      min_samples_leaf: 5
      max_depth: 10
      keep_gfr: true
      variance_forest_num_trees: 50
      random_effects_group: .split_group
      num_gfr: 0
      num_burnin: 100
      num_mcmc: 200
      variance_forest: true
      random_effects: false
    rebart:
      num_trees: 75
      alpha: 0.95
      beta: 2
      min_samples_leaf: 5
      max_depth: 10
      keep_gfr: true
      variance_forest_num_trees: 50
      random_effects_group: .split_group
      num_gfr: 0
      num_burnin: 100
      num_mcmc: 200
      variance_forest: false
      random_effects: true
    knn:
      k: 10
    cubist:
      committees: 1
      neighbors: 0
    svr:
      C: 1
      epsilon: 0.1
    qrf:
      num_trees: 500
      mtry: ~
      min_node_size: 10
      max_depth: ~
      sample_fraction: 1
      replace: true
      quantile: 0.9
    gpr:
      var: 0.001
    mean: []
  n_folds: 5
  inner_folds: 5
  workers: 1
  outcome_col: error_abs_log
  outcome_clip_quantile: 0.99
  outcome_transform: log1p
  lambda_rule: lambda.1se
  loss: squared_error
selection:
  one_se_multiplier: 1.0
  equivalence_tolerance: 0.05
  n_boot: 500
  seed: ~
  uncertainty_rule: tolerance
  u_tol_rel: 0.25
  u_tol_abs: 0.05
  uncertainty_relative_tolerance: 0.25
  uncertainty_absolute_tolerance: 0.05
  local_distance_tolerance: 1.0e-12
  conformal_alpha: 0.1
  bin_alpha: 0.1
  min_bin_scores: 10
  n_bins: 3
  use_support_bin_intervals: false
  support_bin_labels:
  - Lower support
  - Moderate support
  - Higher support
  method: glm
  super_methods: ~
  method_settings:
    glm: []
    glm_ridge:
      standardize: true
      type_measure: mae
      alpha: 0
    glm_lasso:
      standardize: true
      type_measure: mae
      alpha: 1
    glm_elastic:
      standardize: true
      type_measure: mae
      alpha: 0.25
    qreg:
      tau: 0.5
      fit_method: fn
    gam:
      fit_method: REML
      select_terms: true
    lmm:
      fit_method: REML
      random_intercept: .split_group
    rpart:
      cp: 0.01
      minsplit: 20
      minbucket: 7
      maxdepth: 30
    rf:
      num_trees: 500
      mtry: ~
      min_node_size: 5
      max_depth: ~
      sample_fraction: 1
      replace: true
      respect_unordered_factors: order
    xgboost:
      nrounds: 100
      eta: 0.3
      max_depth: 6
      min_child_weight: 1
      subsample: 1
      colsample_bytree: 1
      lambda: 1
      alpha: 0
      nthread: 1
    mars:
      degree: 2
      penalty: 3
      nprune: ~
      pmethod: backward
    bart:
      num_trees: 75
      alpha: 0.95
      beta: 2
      min_samples_leaf: 5
      max_depth: 10
      keep_gfr: true
      variance_forest_num_trees: 50
      random_effects_group: .split_group
      num_gfr: 0
      num_burnin: 100
      num_mcmc: 200
      variance_forest: false
      random_effects: false
    xbart:
      num_trees: 75
      alpha: 0.95
      beta: 2
      min_samples_leaf: 5
      max_depth: 10
      keep_gfr: true
      variance_forest_num_trees: 50
      random_effects_group: .split_group
      num_gfr: 40
      num_burnin: 0
      num_mcmc: 0
      variance_forest: false
      random_effects: false
    wsbart:
      num_trees: 75
      alpha: 0.95
      beta: 2
      min_samples_leaf: 5
      max_depth: 10
      keep_gfr: true
      variance_forest_num_trees: 50
      random_effects_group: .split_group
      num_gfr: 20
      num_burnin: 0
      num_mcmc: 200
      variance_forest: false
      random_effects: false
    vfbart:
      num_trees: 75
      alpha: 0.95
      beta: 2
      min_samples_leaf: 5
      max_depth: 10
      keep_gfr: true
      variance_forest_num_trees: 50
      random_effects_group: .split_group
      num_gfr: 0
      num_burnin: 100
      num_mcmc: 200
      variance_forest: true
      random_effects: false
    rebart:
      num_trees: 75
      alpha: 0.95
      beta: 2
      min_samples_leaf: 5
      max_depth: 10
      keep_gfr: true
      variance_forest_num_trees: 50
      random_effects_group: .split_group
      num_gfr: 0
      num_burnin: 100
      num_mcmc: 200
      variance_forest: false
      random_effects: true
    knn:
      k: 10
    cubist:
      committees: 1
      neighbors: 0
    svr:
      C: 1
      epsilon: 0.1
    qrf:
      num_trees: 500
      mtry: ~
      min_node_size: 10
      max_depth: ~
      sample_fraction: 1
      replace: true
      quantile: 0.9
    gpr:
      var: 0.001
    mean: []
  n_folds: 5
  inner_folds: 5
  workers: 1
  outcome_col: error_abs_log
  outcome_clip_quantile: 0.99
  outcome_transform: log1p
  lambda_rule: lambda.1se
  loss: squared_error
  max_selection_tolerance: 1.0e-12
simulation:
  workers: 1
)--",
  r = r"--(list(
  paths = list(
    input_file = "input.xlsx",
    out_root = "outputs",
    cache_dir = "cache",
    supplemental_dir = "supplemental",
    log_file = "outputs/tsbiomass_run.log"
  ),
  execution = list(
    strict_length_pdf = FALSE,
    run_multiplier_model = FALSE,
    write_log = FALSE,
    progress = FALSE
  ),
  tuning = list(
    max_models_per_species = 2,
    n_resamples = 8,
    n_cores = 1,
    seed = NULL,
    alpha_range = list(
      from = 0.1,
      to = 0.9
    ),
    kernel_scale_range = list(
      from = 1,
      to = 8
    ),
    coherence = list(
      length = list(range = list(from = 0.5, to = 6)),
      depth = list(range = list(from = 0.5, to = 6)),
      frequency = list(range = list(from = 0.5, to = 6))
    ),
    grid_refinement_levels = 1,
    response_surface_top_n = 20,
    rmse_tolerance = 0.01,
    support_strata_bins = 4,
    regularization = list(
      alpha = 0.05,
      kernel_scale = 0.05,
      coherence_scale = 0.05,
      stability = 0.02
    ),
    equal_start_weights = FALSE
  ),
  similarity = list(
    alpha = 0.8,
    kernel_scale = 4,
    species_traits = list(
      class = 1
    ),
    study_traits = list(
      fao_area = 1
    ),
    coherence = list(
      length = list(
        mode = "overlap",
        weight = 2
      ),
      depth = list(
        mode = "overlap",
        weight = 3
      ),
      frequency = list(
        mode = "overlap",
        weight = 2,
        gap = 60
      )
    ),
    conformal_alpha = 0.1
  ),
  ordination = list(
    include_loadings = FALSE,
    include_centroids = FALSE
  ),
  policies = list(
    group = list("species"),
    metric = list("closest"),
    slope_class = list("all")
  ),
  cache = list(
    folder = "cache",
    refresh = FALSE,
    names = list(
      worms = "worms_species_traits.rds",
      fishbase = "fishbase_species_traits.rds",
      pelagic = "pelagic_species_traits.rds",
      azores = "azores_species_traits.rds",
      continental = "continental_species_traits.rds",
      mstraits = "mstraits_species_traits.rds",
      species_enriched = "species_traits_enriched.rds",
      candidate_models = "candidate_models_prepared.rds",
      similarity_tuning = "similarity_tuning.rds",
      anchor_admissibility = "anchor_admissibility.rds",
      policy_benchmark = "policy_benchmark.rds",
      policy_conformal = "policy_conformal.rds",
      policy_selection = "policy_selection.rds",
      policy_sensitivity = "policy_sensitivity.rds"
    )
  ),
  benchmark = list(
    workers = 1,
    engine = "cpp",
    include_ts_error = FALSE
  ),
  admissibility = list(
    species_traits = character(0),
    study_traits = character(0),
    coherence = list(
      length = list(
        mode = "overlap",
        min = 0.25
      ),
      depth = list(
        mode = "overlap",
        min = 0.25
      ),
      frequency = list(
        mode = "none",
        gap = 60
      )
    ),
    key_metadata_max = 0.25
  ),
  uncertainty = list(
    method = "glm",
    super_methods = NULL,
    method_settings = list(
      glm = list(),
      glm_ridge = list(
        standardize = TRUE,
        type_measure = "mae",
        alpha = 0
      ),
      glm_lasso = list(
        standardize = TRUE,
        type_measure = "mae",
        alpha = 1
      ),
      glm_elastic = list(
        standardize = TRUE,
        type_measure = "mae",
        alpha = 0.25
      ),
      qreg = list(
        tau = 0.5,
        fit_method = "fn"
      ),
      gam = list(
        fit_method = "REML",
        select_terms = TRUE
      ),
      lmm = list(
        fit_method = "REML",
        random_intercept = ".split_group"
      ),
      rpart = list(
        cp = 0.01,
        minsplit = 20,
        minbucket = 7,
        maxdepth = 30
      ),
      rf = list(
        num_trees = 500,
        mtry = NULL,
        min_node_size = 5,
        max_depth = NULL,
        sample_fraction = 1,
        replace = TRUE,
        respect_unordered_factors = "order"
      ),
      xgboost = list(
        nrounds = 100,
        eta = 0.3,
        max_depth = 6,
        min_child_weight = 1,
        subsample = 1,
        colsample_bytree = 1,
        lambda = 1,
        alpha = 0,
        nthread = 1
      ),
      mars = list(
        degree = 2,
        penalty = 3,
        nprune = NULL,
        pmethod = "backward"
      ),
      bart = list(
        num_trees = 75,
        alpha = 0.95,
        beta = 2,
        min_samples_leaf = 5,
        max_depth = 10,
        keep_gfr = TRUE,
        variance_forest_num_trees = 50,
        random_effects_group = ".split_group",
        num_gfr = 0,
        num_burnin = 100,
        num_mcmc = 200,
        variance_forest = FALSE,
        random_effects = FALSE
      ),
      xbart = list(
        num_trees = 75,
        alpha = 0.95,
        beta = 2,
        min_samples_leaf = 5,
        max_depth = 10,
        keep_gfr = TRUE,
        variance_forest_num_trees = 50,
        random_effects_group = ".split_group",
        num_gfr = 40,
        num_burnin = 0,
        num_mcmc = 0,
        variance_forest = FALSE,
        random_effects = FALSE
      ),
      wsbart = list(
        num_trees = 75,
        alpha = 0.95,
        beta = 2,
        min_samples_leaf = 5,
        max_depth = 10,
        keep_gfr = TRUE,
        variance_forest_num_trees = 50,
        random_effects_group = ".split_group",
        num_gfr = 20,
        num_burnin = 0,
        num_mcmc = 200,
        variance_forest = FALSE,
        random_effects = FALSE
      ),
      vfbart = list(
        num_trees = 75,
        alpha = 0.95,
        beta = 2,
        min_samples_leaf = 5,
        max_depth = 10,
        keep_gfr = TRUE,
        variance_forest_num_trees = 50,
        random_effects_group = ".split_group",
        num_gfr = 0,
        num_burnin = 100,
        num_mcmc = 200,
        variance_forest = TRUE,
        random_effects = FALSE
      ),
      rebart = list(
        num_trees = 75,
        alpha = 0.95,
        beta = 2,
        min_samples_leaf = 5,
        max_depth = 10,
        keep_gfr = TRUE,
        variance_forest_num_trees = 50,
        random_effects_group = ".split_group",
        num_gfr = 0,
        num_burnin = 100,
        num_mcmc = 200,
        variance_forest = FALSE,
        random_effects = TRUE
      ),
      knn = list(
        k = 10
      ),
      cubist = list(
        committees = 1,
        neighbors = 0
      ),
      svr = list(
        C = 1,
        epsilon = 0.1
      ),
      qrf = list(
        num_trees = 500,
        mtry = NULL,
        min_node_size = 10,
        max_depth = NULL,
        sample_fraction = 1,
        replace = TRUE,
        quantile = 0.9
      ),
      gpr = list(
        var = 0.001
      ),
      mean = list()
    ),
    n_folds = 5,
    inner_folds = 5,
    workers = 1,
    outcome_col = "error_abs_log",
    outcome_clip_quantile = 0.99,
    outcome_transform = "log1p",
    lambda_rule = "lambda.1se",
    loss = "squared_error"
  ),
  selection = list(
    one_se_multiplier = 1,
    equivalence_tolerance = 0.05,
    n_boot = 500,
    seed = NULL,
    uncertainty_rule = "tolerance",
    u_tol_rel = 0.25,
    u_tol_abs = 0.05,
    uncertainty_relative_tolerance = 0.25,
    uncertainty_absolute_tolerance = 0.05,
    local_distance_tolerance = 1e-12,
    conformal_alpha = 0.1,
    bin_alpha = 0.1,
    min_bin_scores = 10,
    n_bins = 3,
    use_support_bin_intervals = FALSE,
    support_bin_labels = c("Lower support", "Moderate support", "Higher support"),
    method = "glm",
    super_methods = NULL,
    method_settings = list(
      glm = list(),
      glm_ridge = list(
        standardize = TRUE,
        type_measure = "mae",
        alpha = 0
      ),
      glm_lasso = list(
        standardize = TRUE,
        type_measure = "mae",
        alpha = 1
      ),
      glm_elastic = list(
        standardize = TRUE,
        type_measure = "mae",
        alpha = 0.25
      ),
      qreg = list(
        tau = 0.5,
        fit_method = "fn"
      ),
      gam = list(
        fit_method = "REML",
        select_terms = TRUE
      ),
      lmm = list(
        fit_method = "REML",
        random_intercept = ".split_group"
      ),
      rpart = list(
        cp = 0.01,
        minsplit = 20,
        minbucket = 7,
        maxdepth = 30
      ),
      rf = list(
        num_trees = 500,
        mtry = NULL,
        min_node_size = 5,
        max_depth = NULL,
        sample_fraction = 1,
        replace = TRUE,
        respect_unordered_factors = "order"
      ),
      xgboost = list(
        nrounds = 100,
        eta = 0.3,
        max_depth = 6,
        min_child_weight = 1,
        subsample = 1,
        colsample_bytree = 1,
        lambda = 1,
        alpha = 0,
        nthread = 1
      ),
      mars = list(
        degree = 2,
        penalty = 3,
        nprune = NULL,
        pmethod = "backward"
      ),
      bart = list(
        num_trees = 75,
        alpha = 0.95,
        beta = 2,
        min_samples_leaf = 5,
        max_depth = 10,
        keep_gfr = TRUE,
        variance_forest_num_trees = 50,
        random_effects_group = ".split_group",
        num_gfr = 0,
        num_burnin = 100,
        num_mcmc = 200,
        variance_forest = FALSE,
        random_effects = FALSE
      ),
      xbart = list(
        num_trees = 75,
        alpha = 0.95,
        beta = 2,
        min_samples_leaf = 5,
        max_depth = 10,
        keep_gfr = TRUE,
        variance_forest_num_trees = 50,
        random_effects_group = ".split_group",
        num_gfr = 40,
        num_burnin = 0,
        num_mcmc = 0,
        variance_forest = FALSE,
        random_effects = FALSE
      ),
      wsbart = list(
        num_trees = 75,
        alpha = 0.95,
        beta = 2,
        min_samples_leaf = 5,
        max_depth = 10,
        keep_gfr = TRUE,
        variance_forest_num_trees = 50,
        random_effects_group = ".split_group",
        num_gfr = 20,
        num_burnin = 0,
        num_mcmc = 200,
        variance_forest = FALSE,
        random_effects = FALSE
      ),
      vfbart = list(
        num_trees = 75,
        alpha = 0.95,
        beta = 2,
        min_samples_leaf = 5,
        max_depth = 10,
        keep_gfr = TRUE,
        variance_forest_num_trees = 50,
        random_effects_group = ".split_group",
        num_gfr = 0,
        num_burnin = 100,
        num_mcmc = 200,
        variance_forest = TRUE,
        random_effects = FALSE
      ),
      rebart = list(
        num_trees = 75,
        alpha = 0.95,
        beta = 2,
        min_samples_leaf = 5,
        max_depth = 10,
        keep_gfr = TRUE,
        variance_forest_num_trees = 50,
        random_effects_group = ".split_group",
        num_gfr = 0,
        num_burnin = 100,
        num_mcmc = 200,
        variance_forest = FALSE,
        random_effects = TRUE
      ),
      knn = list(
        k = 10
      ),
      cubist = list(
        committees = 1,
        neighbors = 0
      ),
      svr = list(
        C = 1,
        epsilon = 0.1
      ),
      qrf = list(
        num_trees = 500,
        mtry = NULL,
        min_node_size = 10,
        max_depth = NULL,
        sample_fraction = 1,
        replace = TRUE,
        quantile = 0.9
      ),
      gpr = list(
        var = 0.001
      ),
      mean = list()
    ),
    n_folds = 5,
    inner_folds = 5,
    workers = 1,
    outcome_col = "error_abs_log",
    outcome_clip_quantile = 0.99,
    outcome_transform = "log1p",
    lambda_rule = "lambda.1se",
    loss = "squared_error",
    max_selection_tolerance = 1e-12,
    refresh = FALSE
  ),
  simulation = list(
    workers = 1
  )
))--")
```
