---
title: "Empirical Similarity Tuning"
description: >
  Configuration and parameterization notes for the Candidates empirical
  similarity-tuning path.
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Empirical Similarity Tuning}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", eval = FALSE)
```

The empirical path keeps distance construction explicit. The `similarity`
section defines the baseline trait set, trait weights, coherence weights,
`alpha`, and `kernel_scale`. The `tuning` section then defines how
`tune_similarities()` searches around that baseline using leave-one-out
transfer error.

Use this path when you want direct control over which biological and study
traits contribute to donor similarity, or when there are not enough anchors to
fit a stable supervised Alchemist model.

```{r}
cfg <- create_configuration_template()

cfg$similarity <- list(
  alpha = 0.7,
  kernel_scale = 3,
  species_traits = list(genus = 1, family = 1, trophic = 0.5),
  study_traits = list(frequency = 1, fao_area = 1),
  coherence = list(
    length = list(mode = "overlap", weight = 2),
    depth = list(mode = "overlap", weight = 2),
    frequency = list(mode = "overlap", weight = 1, gap = 60)
  ),
  conformal_alpha = 0.1
)

cfg$tuning <- list(
  max_models_per_species = 2,
  n_resamples = 8,
  n_cores = 4,
  alpha_range = list(from = 0.4, to = 0.9),
  kernel_scale_range = list(from = 1, to = 6),
  coherence = list(
    length = list(range = list(from = 0.5, to = 6)),
    depth = list(range = list(from = 0.5, to = 6)),
    frequency = list(range = list(from = 0.25, to = 4))
  ),
  equal_start_weights = FALSE,
  seed = 20260702
)

config <- build_configurer(cfg)
candidates <- build_candidates(config)
candidates <- prepare_similarities(candidates, config = config)
candidates <- tune_similarities(candidates, config = config)
```

Parameter ownership is intentionally split:

- `similarity.species_traits` and `similarity.study_traits` select the traits
  and set their starting weights.
- `similarity.coherence.*.weight` sets the starting weights for length, depth,
  and frequency coherence features.
- `tuning.alpha_range` and `tuning.kernel_scale_range` define empirical search
  bounds for the scalar similarity parameters.
- `tuning.coherence.*.range` defines empirical search bounds for coherence
  weights.
- Trait-weight adjustment is handled by the component-impact pass after the
  scalar search; selected trait starting weights in `similarity` are the prior
  weights that this pass rescales.

Keep the search ranges scientifically plausible. If the optimum lands on a
range boundary, widen the range only when the boundary value is defensible; a
boundary optimum is often a sign that the selected traits do not describe the
transfer problem well enough. For sparse anchor sets, prefer fewer traits and
stable priors over large trait lists with aggressive empirical reweighting.
