---
title: "Generalized TS Transferability Pipeline"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Generalized TS Transferability Pipeline}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Purpose

`tsbiomass` now centers the analysis pipeline around a small set of S7 objects instead of a long chain of loosely related lists. The core path is:

1. `Configurer`: validate and normalize one complete configuration.
2. `Candidates`: ingest, enrich, and prepare the candidate model table.
3. `PolicySelector`: benchmark policies, calibrate uncertainty, select globally acceptable policies, and generate anchor-facing predictions.
4. `PolicyLearner` (optional): fit a meta-policy or super-learner that ranks policy choices by predicted transfer risk.
5. `PolicySimulator` (optional): rerun the policy stack across standard sensitivity scenarios.

The point of this interface is not just cleaner code. It also makes the analysis state explicit. Each object carries the staged results needed by the next step.

## Typical Usage

The package supports both explicit R configuration and external YAML configuration.

### From YAML

```{r, eval = FALSE}
library(tsbiomass)

cfg <- configurer_from_yaml("path/to/config.yaml")

candidates <- as_candidates(cfg)
candidates <- set_reference_anchors(candidates)
candidates <- prepare_similarity_matrix(candidates, config = cfg)
candidates <- build_gower_distances(candidates)
candidates <- run_ordination(candidates)
candidates <- tune_similarity_matrix(candidates, config = cfg)
candidates <- screen_admissibility(candidate_models = candidates, config = cfg)

selector <- as_policy_selector(candidates, config = cfg)
selector <- benchmark(selector)
selector <- calibrate_uncertainty(selector)
selector <- select_policies(selector)

predictions <- predict(selector)
predictions@selections
```

### From an explicit R list

```{r, eval = FALSE}
cfg <- as_configurer(list(
  paths = list(
    input_file = "input.xlsx",
    out_root = "outputs",
    cache_dir = "cache"
  ),
  execution = list(
    strict_length_pdf = FALSE,
    run_multiplier_model = FALSE,
    write_log = FALSE
  ),
  tuning = list(
    max_models_per_species = 2L,
    n_resamples = 8L
  ),
  policy = list(
    alpha = 0.8,
    k_species = 4,
    k_study = 2,
    frequency_coherence_mode = "numeric",
    require_same_frequency_label = FALSE,
    max_frequency_gap_khz = 60,
    min_length_overlap_fraction = 0.25,
    min_depth_overlap_fraction = 0.25,
    missing_key_metadata_max_fraction = 0.25,
    length_overlap_weight = 2,
    depth_overlap_weight = 2,
    frequency_coherence_weight = 1,
    core_weight_cutoff = 0.8,
    conformal_alpha = 0.1,
    species_traits = list(genus = 1, family = 0.5),
    study_traits = list(frequency = 1, fao_area = 1)
  ),
  policies = list(
    active = c("same_species_closest", "same_genus_weighted")
  )
))
```

## What Each Object Does

### `Configurer`

`Configurer` is the configuration boundary. It validates:

- required sections
- policy trait weights against the trait registry
- policy names against the policy registry
- scalar tuning and admissibility settings
- path fields and top-level structural consistency

The constructor does not inject an analysis-specific template. The caller must supply the configuration explicitly, either as YAML or as a nested R list.

### `Candidates`

`Candidates` is the main staged data object. It carries:

- the raw study table
- the ingested source tables
- the enriched species table
- the prepared candidate model table
- the selected reference anchors
- any prepared similarity, distance, ordination, admissibility, and tuning results

In practice, that means downstream functions do not need to rebuild the entire ingest or enrichment context just to continue the analysis.

### `PolicySelector`

`PolicySelector` owns the policy-evaluation path:

- `benchmark()` runs the anchor-based policy benchmark
- `calibrate_uncertainty()` fits policy-level conformal widths
- `select_policies()` builds the global policy screen
- `predict()` applies the current policy set back to the retained anchors

The output of `predict()` is a `PolicyPredictions` object with:

- `intervals`: every anchor-policy prediction row
- `selections`: the retained display row per anchor
- `consensus`: the donor-pool baseline summaries

### `PolicyLearner`

`PolicyLearner` is optional. It is used when deterministic policy selection is replaced by a risk model that predicts which policy is likely to transfer best for a given anchor.

The intended sequence is:

```{r, eval = FALSE}
learner <- as_policy_learner(selector)
learner <- crossfit(learner)
learner <- fit(learner)
learner <- calibrate_uncertainty(learner)

meta_predictions <- predict(selector, learner = learner)
```

The selector still remains the single outward-facing prediction entry point.

### `PolicySimulator`

`PolicySimulator` reruns the benchmark, conformal, and selection stack across standard sensitivity scenarios:

```{r, eval = FALSE}
simulator <- as_policy_simulator(selector)
simulator <- simulate(simulator)

build_sensitivity_table(simulator)
bind_sensitivity_data(simulator)
```

This keeps the baseline analysis and the scenario reruns in one consistent object layer.

## Similarity Mathematics

### Trait Preparation

The pipeline begins by separating **species-level traits** from **study-level traits**.

- Species-level traits describe biological similarity, such as taxonomic position or swimbladder type.
- Study-level traits describe survey or equation context, such as frequency or FAO area.

Set-valued traits are expanded into binary membership columns before distance calculation. That keeps the representation explicit instead of hiding set overlap inside ad hoc string logic.

### Weighted Gower Distances

For each block, the package builds a weighted Gower distance:

\[
d_{ij}^{(\mathrm{species})}
\quad \text{and} \quad
d_{ij}^{(\mathrm{study})}
\]

where the per-trait contributions are weighted by the configured trait weights.

For interval-like variables, such as length and depth ranges, the package uses overlap-derived pairwise components rather than treating the endpoints as unrelated scalar fields.

### Combined Similarity Matrix

The species and study distances are combined through the mixing parameter \(\alpha\):

\[
d_{ij}^{(\mathrm{combined})}
=
\frac{
\alpha \, d_{ij}^{(\mathrm{species})}
+
(1-\alpha) \, d_{ij}^{(\mathrm{study})}
}{
\alpha \, I_{ij}^{(\mathrm{species})}
+
(1-\alpha) \, I_{ij}^{(\mathrm{study})}
}
\]

where each indicator \(I_{ij}\) is one when that component is available for the pair and zero otherwise. This renormalization matters: if one block is missing for a pair, the pipeline does not let the missing block silently force the full combined distance to `NA`.

### Tuning

`tune_similarity_matrix()` tunes:

- \(\alpha\)
- the species kernel scale \(k_{\text{species}}\)
- the study kernel scale \(k_{\text{study}}\)
- the effective importance of individual traits and coherence terms

The current implementation uses a coarse grid followed by local refinement around the best region, so the search can become denser near promising values without paying for a uniformly dense global grid.

## Admissibility Logic

Admissibility is not just “nearest model wins.” Each anchor is screened against the candidate pool with explicit gates, including:

- self-donor exclusion
- overlap in length range
- overlap in depth range
- key-metadata missingness thresholds
- structural or biological constraints, such as swimbladder matching where required

This stage produces both the filtered donor pool and the detailed gate diagnostics used later in the audit tables and plots.

## Policy Benchmark and Selection

Policies are benchmarked on held-out anchors. For each anchor-policy combination, the pipeline computes a predicted multiplier and compares it with the anchor truth on the log scale:

\[
e = \log(\widehat{m}) - \log(m)
\]

The main summary scale is the absolute log error:

\[
|e| = \left| \log(\widehat{m}) - \log(m) \right|
\]

This choice matters because multiplicative biomass error is naturally symmetric on the log scale. Over-predicting by a factor of two and under-predicting by a factor of two are then treated consistently.

`select_policies()` summarizes policy performance across species-block validation and retains the globally acceptable or equivalent-to-best policies for downstream display.

## Conformal Policy Intervals

The uncertainty layer calibrates multiplicative intervals from policy-specific absolute log residuals. If \(q_\alpha\) is the calibrated quantile of \(|e|\), then a point prediction \(\widehat{m}\) is expanded to:

\[
\left[
\widehat{m}\exp(-q_\alpha),
\widehat{m}\exp(q_\alpha)
\right]
\]

This is why the package stores uncertainty widths on the **log-multiplier** scale. The intervals are multiplicative in biomass space even though calibration is performed on absolute log residuals.

## Meta-Policy Learning

When a single global policy rule is too blunt, `PolicyLearner` fits a meta-model that predicts policy risk from anchor-policy features such as:

- local donor support
- local combined distance
- structural spread
- counts of valid or biologically close donors

Cross-fitting is used so each prediction is out-of-fold with respect to its anchor group. Post-selection conformal calibration is then applied to the selected rows, either pooled across all selected rows or stratified by support bins.

## Sensitivity Scenarios

`PolicySimulator` automates reruns of the policy stack under standard perturbations, such as:

- altered overlap cutoffs
- altered missingness thresholds
- altered similarity or coherence settings
- candidate-pool restrictions

The main outputs are:

- a manifest describing every scenario
- scenario-bound policy-selection tables
- scenario-bound conformal tables
- scenario-bound equivalence summaries

This makes it possible to audit whether the displayed recommendation is stable or changes materially under reasonable perturbations.

## Practical Reading of the Pipeline

In plain terms, the package answers four questions in order:

1. Which models are even plausible donors for this anchor?
2. Among plausible donors, which policies transfer best on held-out data?
3. How uncertain are the resulting multiplier recommendations?
4. Does the answer stay stable under sensible perturbations?

The S7 refactor keeps each of those stages explicit and inspectable instead of burying them inside one large packaged script.
